Umiddelbart er vi ikke kommet nærmere hvilke $x$, der opfylder \eqref{eq:Betingelse}. Vi kan dog se at vi har nogle modstrider. For i nogle af vores min terms vil have at tallet vi leder efter skal vaere baade et primtal og have at $gcd(x,2)$ er forskelig fra et dvs sige at den skal vaere 2. Tallet skal derfor baade vaere et primtal og et lige tal. Dette er noget der kun gaelder for 2. Man kan altsaa reducere til foelgende. 

\begin{equation}
    (\neg P \wedge R \wedge \neg Q)\vee(\neg P \wedge \neg R \wedge Q)
\end{equation}


\section{Task 3}
\subsection{Subtask 1}
\noindent
\textbf{Bevis følgende sætning: Lad $x$ være et positivt heltal. At $\gcd(x,2)=1$ er ækvivalent med, at $x$ er ulige.}

\bigskip
\noindent
\textbf{Solution:} We assume that $x=2n$ and that $gcd(x,2)=1$. If the previous two are true it means that 2 does not divide x. However, x is even meaning that we can write is $2n$ clearly seing that it is divisible by 2. We now have a contradiction, thus if $gcd(x,2)=1$ x has to be odd.

\subsection{Subtask 2}
\noindent
\textbf{Forklar hvorfor, at ovenstående betyder, at $Q(x)$ reelt set er det samme som $R(x)$. Derfor kan vi erstatte $R(x)$ med $Q(x)$ i \eqref{eq:Betingelse} og opnå, at \eqref{eq:Betingelse} er ækvivalent med
	\begin{align}\label{eq:BetingelseReduceret}
		&(P(x)\wedge \neg Q(x)) \vee \neg(P(x)\vee \neg Q(x) \vee Q(x)) \vee (\neg P(x) \wedge \neg Q(x) \wedge Q(x)) \nonumber\\ 
		\equiv& (P(x)\wedge \neg Q(x)) \vee \neg(P(x)\vee \mathbb{T}) \vee (\neg P(x) \wedge \mathbb{F}) \nonumber\\
		\equiv& P(x)\wedge \neg Q(x)
	\end{align}
}

\bigskip
\noindent
\textbf{Solution:} This means that if Q(x) is true x is odd on if Q(x) is false x is even. If we say that $9^1=n$ we get that $n mod 5 = 4$ for Q(x) be true. Now i just have to show that $9^x = 5m+4$ when x is odd and that it doesn't when it's even. I start with the base cases of $x=1$ and $x=2$.

\begin{equation}
    \begin{aligned}
        9=5+4=5 \cdot m+4 \\
        9^2=81=16 \cdot 5+1=5 \cdot m+1
    \end{aligned}
\end{equation}

Now for the subsequent cases we show that result does not change when we add 2 to the value of x.

\begin{equation}
    \begin{aligned}
        9^{x+2} \\
        9^x \cdot 9^2
    \end{aligned}
\end{equation} 

Now we have that $9^x$ x can either be odd or even if odd we assume that we get $5m+4$ and if even we assume $5m+1$ we know that $9^2=5m+1$ so let's see if the results change.

\begin{equation}
    \begin{aligned}
        (5m + 4) \cdot (5m + 1) \\ 
        (5m)^2 + 5m + 5 \cdot 4m + 4 \\
        5 \cdot (5m^2 + m + 4m) + 4
    \end{aligned}
\end{equation} 

\begin{equation}
    \begin{aligned}
        (5m + 1) \cdot (5m + 1) \\ 
        (5m)^2 + 5m + 5m + 1 \\
        5 \cdot (5m^2 + 2m) + 1
    \end{aligned}
\end{equation} 

This are the desired results thus Q(x) have been shown to be equivelant to R(x)

\subsection{Subtask 3}
\noindent
\textbf{Forklar om \eqref{eq:BetingelseReduceret} er på CNF, DNF, PCNF og PDNF.}

\bigskip
\noindent
\textbf{Solution:} PCNF and PDNF are made up of max or min terms (might be the other way around). Both of these terms have to include the statements or their negation exactly once. Since there is no $R(x)$ this can't be PCNF or PDNF. It has to be CNF since both $P(x)$ and $\neg Q(x)$ are elementary disjunctive statements, and CNF is a statement made of conjections of elementary disjunctive statements. 
